Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 draft.tex
abstract tweaks

The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
Preliminary studies show that random job placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
However, in this paper, we made the observation that while random job placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
The performance improvement of communication-intensive applications comes at the expense of performance degradation of less intensive ones. 
We identify this ``bully" behavior and validate its underneath causes with the help of detailed network simulation and real application traces.
We investigate a hybrid job placement policy as an alternative for dragonfly connected systems.
Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.

>>>>

The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
Preliminary studies show that random job placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
However, in this paper, we made the observation that while random job placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
The performance improvement of communication-intensive applications comes at the expense of performance degradation of less intensive ones. 
We identify this ``bully" behavior and validate its underlying causes with the help of detailed network simulation and real application traces.
We investigate a hybrid contiguous-noncontiguous job placement policy as an alternative for dragonfly connected systems.
Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.
